Exploration of Adversarial Training

### 2025-05-13 AIAA2290/report/main.tex
Update AIAA2290 report

\subsection{Projected Gradient Descent}

This method try to construct attack samples using iteration towards the direction that relates to the gradient of loss function w.r.t. the input, 
which is usually the normalized value of $\nabla_{\mathbf{x}}(L(f_\theta(\mathrm{x}+\delta), y))$. People tend to use $l_0, l_2$ and $l_{\infty}$. Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ .

@@

    \While 
    \EndWhile
\end{algorithmic}
\end{breakablealgorithm}

>>>>

\subsection{Projected Gradient Descent (PGD)}

This method try to construct attack samples using iteration towards the direction that relates to the gradient of loss function w.r.t. the input, 
which is usually the normalized value of $\nabla_{\mathbf{x}}(L(f_\theta(\mathrm{x}+\delta), y))$. People tend to use $l_0, l_2$ and $l_{\infty}$. Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ , while the number of step for each generation of attack sample is defined by another hyperparameter $k$ .

For a PGD process with specific number of iteration $k$, we can call it $k$-PGD.

@@

  \For {$n=1$ to $N$}
    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}}$ 
      \State {$\delta\leftarrow$ zero matrix with shape of $X$}
      \For {$t\leftarrow 1$ to $k$}
        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
        \State $\delta\leftarrow \mathrm{clamp}(\delta + \alpha g_a, -\epsilon, \epsilon)$
      \EndFor
      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
      \State $\theta \leftarrow \theta - \tau g_\theta$
    \EndFor
  \EndFor
\end{algorithmic}
\end{breakablealgorithm}

Overall, the times of forward propagation and backpropagation of this algorithm are both $\Theta (NMk)$, where $M$ is the number of mini-batches

\subsection{You can Only Propagate Once (YOPO)}

To increase the efficience of adversarial training,
